# To view this dashboard, you need to first run the program and then knit the document
# Please install the required pacakages, if runtime throws errors by uncommenting below line-
# install.packages(c("flexdashboard", "knitr", "DT", "rpivotTable","ggplot2", "plotly", "dplyr", "openintro", "ggvis", "highcharter"))

# Define the libraries you want to install
libraries <- c("flexdashboard", "knitr", "DT", "rpivotTable","ggplot2", "plotly", "dplyr", "openintro", "ggvis", "highcharter")

# Loop through the libraries and install them silently
for (lib in libraries) {
  # Check if the library is already installed
  if (!require(lib, character.only = TRUE)) {
    # Install the library from CRAN without any output or messages
    install.packages(lib, repos = "https://cran.r-project.org", quiet = TRUE, verbose = FALSE)
    # Load the library silently
    suppressPackageStartupMessages(library(lib, character.only = TRUE))
  }
}

---
output:
  flexdashboard::flex_dashboard: default
  pdf_document: default
  html_document: default
---

---
title:  "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: [ "twitter", "facebook", "menu"]
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
```


```{r}
data <- read.csv("https://github.com/bkrai/R-files-from-YouTube/raw/main/vehicle.csv")
```

```{r}
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")
```

Interactive Data Visualization
=====================================

Row
-------------------------------------

### Car Failure Analysis

```{r}
valueBox(paste("Failure"),
         color = "warning")
```

### Car Failures in US

```{r}
valueBox(length(data$State),
         icon = "fa-user")
```

### **Labor Cost**

```{r}
gauge(round(mean(data$lc),
            digits = 2),
            min = 0,
            max = 350,
            gaugeSectors(success = c(0, 150),
                         warning = c(150, 240),
                         danger = c(240, 350),
                         colors = c("green", "yellow", "red")))
```

### Massachusetts

```{r}
valueBox(sum(data$State == "MA"),
         icon = 'fa-building')
```

### California

```{r}
valueBox(sum(data$State == "CA"),
         icon = 'fa-building')
```

### Texas

```{r}
valueBox(sum(data$State == "TX"),
         icon = 'fa-building')
```

### Florida

```{r}
valueBox(sum(data$State == "FL"),
         icon = 'fa-building')
```

Row
-------------------------------

### Failures By State

```{r}
p1 <- data %>%
         group_by(State) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~State,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Failures By State"),
yaxis = list(title = 'Count'))
p1
```

### Top States

```{r}
p2 <- data %>%
         group_by(State) %>%
         summarise(count = n()) %>%
         filter(count>50) %>%
         plot_ly(labels = ~State,
                 values = ~count,
                 marker = list(colors = mycolors)) %>%
         add_pie(hole = 0.2) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                             showgrid=F))
p2
```

### FM Vs Mileage

```{r}
p3 <- plot_ly(data,
              x = ~fm,
              y = ~Mileage,
              text = paste("FM:", data$fm,
                           "Mileage:",
                           data$Mileage),
              type = "bar") %>%
         layout(xaxis = list(title="FM"),
                yaxis = list(title = "Failure Mileage"))
p3
```

Row
------------------------------------
### Scatter Plot of Month Vs Mileage

```{r}
p4 <- plot_ly(data, x=~fm) %>%
         add_markers(y = ~Mileage,
                     text = ~paste("Mileage: ", Mileage),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(Mileage ~ fm)),
                   name = "Loess Smoother",
                   color = I("#FFC125"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Month"),
                yaxis = list(title = "Mileage"))
p4
```

### Box Plot of Top State

```{r}
data %>%
         group_by(State) %>%
         ggvis(~State, ~lc, fill = ~State) %>%
         layer_boxplots()
```